Trajectory Classification

### 2023-03-08 x_trj-classification-segmentation.qmd
heuristic for ARR or DEP assignmnt

```{r}
mst <- baws |> identify_legs() |> make_uid() |> 
  group_by(UID) |> 
  group_modify(.f = ~ init_milestone_table(.x))
```

@@

>>>>

```{r}
baws <- baws |> identify_legs() |> make_uid() 
mst <- baws |> 
  group_by(UID) |> 
  group_modify(.f = ~ init_milestone_table(.x))
```

@@

BAW74 - ICAO24 c("400615")

checking first for overhead threshold

```{r}
fb <- baws |> filter(ICAO24 %in% c("400615")) |> cast_latlon_to_pts(.drop_coord = FALSE)

over_thr <- fb[rwys_egll_pts_buf,]

ggplot() +
  geom_sf(data = rwys_egll_pts, size = 3) +
  geom_sf(data = rwys_egll_pts_buf, color = "blue", fill = NA) +
  geom_sf(data = over_thr, color = "yellow")
```

trajectory points that fall within buffered threshold polygons

```{r}
my_trj <- fb
my_thres_buf <- rwys_egll_pts_buf

check_thr_mst <- function(.trj, .thres_buf){
  this_mst <- st_join(.trj, .thres_buf["REF"], left = FALSE) |> 
  select(ICAO24, FLTID, TIME, LAT, LON, ALT_B, REF) |> 
  mutate(MST = "THR") |> 
  mutate(
        LEAD = geometry[row_number() + 1]
      , DIST = st_distance(geometry, LEAD, by_element = T)
      , DIST = if_else(is.na(DIST), 0, as.numeric(DIST))   #correct for lead/NA
      , CUM_DIST = cumsum(DIST)
      , RLEID = consecutive_id(CUM_DIST)
    ) |> 
  sf::st_drop_geometry() |> 
  filter(TIME == min(TIME), .by = RLEID)
  return(this_mst)
}

thr_mst <- check_thr_mst(my_trj, my_thres_buf)
thr_mst
```

```{r}
baws |> filter(ICAO24 == "40073e") |> cast_latlon_to_pts(.drop_coord = FALSE) |> sf::st_crop(xmin = -1, xmax = 0, ymin = 51.2, ymax = 51.6) |>  ggplot() + geom_point(aes(x = LON, y = LAT)) + geom_sf(data = rwys_egll_pts_buf) 
```

```{r}
baw262 <- baws |> filter(ICAO24 == "40073e")
baw262_ls <- baw262 |> cast_latlon_to_ls() |> sf::st_crop(xmin = -0.5, xmax = 0, ymin = 51.2, ymax = 51.6)

ggplot() +
  geom_sf(data = rwys_egll_box) +
  geom_sf(data = baw262_ls)

```

```{r}
box_poly_sf  <- rwys_egll_box |> sf::st_as_sf() |> mutate(REF = "EGLL-box") |> rename(geometry = x)
this_trj_pts <- baw262 |> cast_latlon_to_pts(.drop_coord = FALSE)

# test with one
baw262 <- sf::st_join(this_trj_pts, box_poly_sf)

key_mst <- baw262 |> filter(MST %in% c("START","END")) |> 
  select(UID, ICAO24, TIME, FLTID, LAT, LON, ALT_B, MST, REF)
key_mst
```
